How the Practice of TDD Influences \\Class Design in Object-Oriented Systems: \\Patterns of Unit Tests Feedback

### 2013-02-26 jss-2013/paper.tex
formatando pro jss
apertando pra caber

% spedoc.tex V3.0, 13 May 2010

\documentclass[times]{speauth}

@@

\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
\pdfminorversion=4
\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\def\volumeyear{2012}

@@

\runningheads{Aniche, Gerosa}{Test-Driven Development}

@@

\keywords{test-driven development, agile software development, class design, object-oriented design}

@@

\vspace{-6pt}

@@

\begin{table}
	\centering
	\begin{tabular}{| p{3cm} | p{6cm} | p{3cm} | }
		\hline
		\textbf{Exercise} & \textbf{Design Smell} & \textbf{Principles to}\\
		& & \textbf{be Followed}\\

@@

\begin{table*}
	\centering
	\begin{tabular}{ | p{2cm} | p{2cm} | p{1.7cm} | p{2cm} | p{1.7cm} | p{1.7cm} |}
		\hline
		\textbf{Exercise} & \textbf{Cyclomatic Complexity} & \textbf{Efferent coupling} & \textbf{Lack of Cohesion of Methods} & \textbf{Number of lines per method} 
		& \textbf{Quantity of methods per class} \\
		\hline
		Exercise 1 &	0.8967	&	0.6741 &	\cellcolor[gray]{0.8}2.04E-07* &	0.4962 &	\cellcolor[gray]{0.8}2.99E-06* \\
		Exercise 2	& 0.7868	&	0.7640 &	0.06132 &	0.9925 &	0.7501 \\
		Exercise 3	& 0.5463	&	0.9872 &	0.5471 &	0.7216 &	0.3972\\
		Exercise 4	& 0.2198	&	0.1361 &	\cellcolor[gray]{0.8}0.04891* &	\cellcolor[gray]{0.8}0.0032* &	0.9358\\
		\hline
		All together &	0.8123	&	0.5604 &	0.3278 &	0.06814 &	0.5849\\
		\hline
	\end{tabular}
	\caption{\textit{P-values} found for the difference between code produced with and without TDD}
	\label{metricas-industria}
\end{table*}

@@

\begin{table}
	\centering
	\begin{tabular}{ | p{5cm} | p{3.5cm} | p{3.5cm} | }
		\hline
		  & \textbf{Experience in TDD} & \textbf{No experience in TDD} \\
		\hline
			\multicolumn{3}{|c|}{Cyclomatic Complexity} \\
		\hline
			Experience in Software Development 		& 0.09933	&	0.8976\\
			\hline
			No Experience in Software Development 	& NA		&	0.4462\\
		\hline
			\multicolumn{3}{|c|}{Fan-Out}\\
		\hline
			Experience in Software Development 		& 0.1401	&	0.6304\\
			\hline
			No Experience in Software Development 	& NA		&	0.2092\\
		\hline
			\multicolumn{3}{|c|}{Lack of Cohesion of Methods}\\
		\hline
			Experience in Software Development 		& \cellcolor[gray]{0.8}0.03061*	&	0.1284\\
			\hline
			No Experience in Software Development 	& NA		&	0.0888\\
		\hline
			\multicolumn{3}{|c|}{Quantity of Methods per Class} \\
		\hline
			Experience in Software Development 		& 0.09933	&	0.8976\\
			\hline
			No Experience in Software Development 	& NA		&	0.4462\\
		\hline
			\multicolumn{3}{|c|}{Lines per Method}\\
		\hline
			Experience in Software Development 		& 0.0513	&	0.4319\\
			\hline
			No Experience in Software Development 	& NA		&	0.5776\\
		\hline
	\end{tabular}
	\caption{\textit{P-values} found for the difference in metrics between experienced and non experienced participants}
	\label{valores-separados}
\end{table}

@@

\begin{table}[h!]
	\centering
	\begin{tabular}{| p{4.5cm} | p{4.5cm} | p{3cm} | }
		\hline

>>>>

\documentclass[times]{elsarticle}

@@

\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
\pdfminorversion=4

@@

@@

@@

@@

\begin{table}
	\centering
	\begin{tabular}{| p{2cm} | p{4cm} | p{2.5cm} | }
		\hline
		\textbf{Exercise} & \textbf{Design Smell} & \textbf{Principles to}\\
		& & \textbf{be Followed}\\

@@

\begin{table*}
	\centering
	\begin{tabular}{ | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} | p{1.5cm} |}
		\hline
		\textbf{Exercise} & \textbf{Cyclomatic Complexity} & \textbf{Efferent coupling} & \textbf{Lack of Cohesion of Methods} & \textbf{Number of lines per method} 
		& \textbf{Quantity of methods per class} \\
		\hline
		Exercise 1 &	0.8967	&	0.6741 &	\cellcolor[gray]{0.8}2.04E-07* &	0.4962 &	\cellcolor[gray]{0.8}2.99E-06* \\
		Exercise 2	& 0.7868	&	0.7640 &	0.06132 &	0.9925 &	0.7501 \\
		Exercise 3	& 0.5463	&	0.9872 &	0.5471 &	0.7216 &	0.3972\\
		Exercise 4	& 0.2198	&	0.1361 &	\cellcolor[gray]{0.8}0.04891* &	\cellcolor[gray]{0.8}0.0032* &	0.9358\\
		\hline
		All together &	0.8123	&	0.5604 &	0.3278 &	0.06814 &	0.5849\\
		\hline
	\end{tabular}
	\caption{\textit{P-values} found for the difference between code produced with and without TDD}
	\label{metricas-industria}
\end{table*}

@@

\begin{table}
	\centering
	\begin{tabular}{ | p{4cm} | p{3cm} | p{3cm} | }
		\hline
		  & \textbf{Experience in TDD} & \textbf{No experience in TDD} \\
		\hline
			\multicolumn{3}{|c|}{Cyclomatic Complexity} \\
		\hline
			Experience in Software Development 		& 0.09933	&	0.8976\\
			\hline
			No Experience in Software Development 	& NA		&	0.4462\\
		\hline
			\multicolumn{3}{|c|}{Fan-Out}\\
		\hline
			Experience in Software Development 		& 0.1401	&	0.6304\\
			\hline
			No Experience in Software Development 	& NA		&	0.2092\\
		\hline
			\multicolumn{3}{|c|}{Lack of Cohesion of Methods}\\
		\hline
			Experience in Software Development 		& \cellcolor[gray]{0.8}0.03061*	&	0.1284\\
			\hline
			No Experience in Software Development 	& NA		&	0.0888\\
		\hline
			\multicolumn{3}{|c|}{Quantity of Methods per Class} \\
		\hline
			Experience in Software Development 		& 0.09933	&	0.8976\\
			\hline
			No Experience in Software Development 	& NA		&	0.4462\\
		\hline
			\multicolumn{3}{|c|}{Lines per Method}\\
		\hline
			Experience in Software Development 		& 0.0513	&	0.4319\\
			\hline
			No Experience in Software Development 	& NA		&	0.5776\\
		\hline
	\end{tabular}
	\caption{\textit{P-values} found for the difference in metrics between experienced and non experienced participants}
	\label{valores-separados}
\end{table}

@@

\begin{table}[h!]
	\centering
	\begin{tabular}{| p{4cm} | p{3.5cm} | p{3cm} | }
		\hline
